CMSAC_reveal_js

### 2025-10-17 CMSAC_presentation/CMSAC_reveal_js.qmd
moved into the correct folder.

```{=html}
<!-- Overall comments 
I think the presentation is too long for 12 minutes (+ questions), but
I feel like I didn't cover everything we want. What is plausable to cover
in a 12-minute period? 
Also, we need to figure out the notation for the final metric because I think
the weight should have the subscript m, not I. And I probably was not consistent
with the usage of theta or calling it true rank/true strength. -->
```

@@

- Other competitions where the correct ranking of some, but not all, of the competitors is of import
  - Olympic competition ranks the top 3 competitors

- "Salient ranks": the ranks of a competition structure that matter
  - Efficacy: 1 through $n$ matter
  - Effectivity: 1 is only salient rank

- We will propose a metric that quantifies how effectively different tournament structures convey information about competitors’ true strengths

>>>>

<!-- Overall comments 
I think the presentation is too long for 12 minutes (+ questions), but
I feel like I didn't cover everything we want. What is plausable to cover
in a 12-minute period? 
Also, we need to figure out the notation for the final metric because I think
the weight should have the subscript m, not I. And I probably was not consistent
with the usage of theta or calling it true rank/true strength. -->

@@

-   Other competitions where the correct ranking of some, but not all, of the competitors is of import
    -   Olympic competition ranks the top 3 competitors
-   "Salient ranks": the ranks of a competition structure that matter
    -   Efficacy: 1 through $n$ matter
    -   Effectivity: 1 is only salient rank
-   We will propose a metric that quantifies how effectively different tournament structures convey information about competitors’ true strengths
